---
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# georefdatar

<!-- badges: start -->
<!-- badges: end -->

The goal of georefdatar is to provide regulary used reference data sets for
geoscience for use with _R_.  

Up to now these are:
* periodic table of the elements
* list of minerals -- with name, symbol (abbreviation) and chemistry
* well known and widely used geochemical data of reservoirs like the primitive
  mantle, to continental crust, basalts, ...
* some functions for basic queries of the periodic table of the elements and the
  list of minerals are also included.

All data sets have full references, making them citable.

## Installation

You can install the development version of georefdatar from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("abuseki/georefdatar")
```

## Example

* To get the classic primitive mantle data of Sun and McDounough (1989) one can use:

  ```{r}
  library(georefdatar)
  
  PM__Sun_McDounough__1989[,c('Cs','Rb','Ba','Th','U','Nb','K','La','Ce','Pb','Pr','Sr','P','Nd','Zr','Sm','Eu','Ti','Dy','Y','Yb','Lu')]
  ```
  
  or using `dplyr`:
  ```{r}
  library(georefdatar)
  library(dplyr)
  
  PM__Sun_McDounough__1989 %>% select(Cs, Rb, Ba, Th, U, Nb, K, La, Ce, Pb, Pr, Sr, P, Nd, Zr, Sm, Eu, Ti, Dy, Y, Yb, Lu)
  ```
  
* Query the list of minerals:
  * by names or symbols given as a regular expression:
    ```{r}
    library(georefdatar)
    
    minSearch('Pyrr.*')
    minSearch('^Ms$')
    ```
  
  * by chemistry as a regular expression:
    ```{r}
    library(georefdatar)

    minsForChemistry('\\(SiO4\\)3$')
    ```

* Query atomic mass from the periodic table of the elements:
  ```{r}
  m('H')
  m('H')*2 + m('O')

  # Si wt% in muscovite
  round(3*m('Si') / (m('K')+3*m('Al')+3*m('Si')+12*m('O')+2*m('H')) * 100, 2)
  ```
  
